Flexibility of interactions depends on habitat suitability

### 2019-09-13 paper/manuscript.Rmd
Remove fake line break from discussion
Add raster and envirem references

Next, we calculate the probability density function of the species distribution in environmental space. 
To determine the environmental space, we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of 0 and a unit standard deviation. 
We then determine the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
We use a kernel method to estimate this density and normalise it such that it ranges between zero and one. 
Specifically, to calculate the probability density function we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@ecospat_citation] with a grid resolution of 200.
We then determine the location in the environmental space of the plant-pollinator communities using the function `suprow` from `ade4`.
The normalised density at that particular location corresponds to our suitability metric, which we calculate using the R package `raster` `r as.character(packageVersion('raster'))` [@raster_citation]. 
We use the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier, as it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.

>>>>

Next, we calculate the probability density function of the species distribution in environmental space. 
To determine the environmental space, we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of 0 and a unit standard deviation. 
We then determine the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
We use a kernel method to estimate this density and normalise it such that it ranges between zero and one. 
Specifically, to calculate the probability density function we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@broennimann_ecospat_2018] with a grid resolution of 200.
We then determine the location in the environmental space of the plant-pollinator communities using the function `suprow` from `ade4`.
The normalised density at that particular location corresponds to our suitability metric, which we calculate using the R package `raster` `r as.character(packageVersion('raster'))` [@hijmans_raster_2019]. 
We use the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier, as it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
